### 2015-09-10 paper.tex
Add comment about strut drag losses
Notes about comparing terms from different measurement areas

Totals for the transport terms in the mean kinetic energy equation---analyzed
identically to \cite{Bachant2015-JoT}---are shown in Fig.~\ref{fig:Ktransport}.
Due to the weaker blade vortex shedding, we see transport due to vertical
advection at this point in the wake is approximately 3 times lower than the
higher solidity UNH-RVAT. We also see relatively lower levels of cross-stream
turbulent transport thanks to the lack of blade stall vortex shedding. These
results may have interesting implications regarding the application of turbines
with lower power coefficient to possibly improve overall array performance
through enhanced transport of kinetic energy from the free stream, though a
detailed anaylsis of the downstream evolution and turbine interaction will be
necessary.

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}
\caption{{\bf Mean Kinetic Energy Transport.}
Estimates for terms contributing to streamwise recovery of mean kinetic energy.}
\label{fig:Ktransport}
\end{figure}

@@

>>>>

Totals for the transport terms in the mean kinetic energy equation---analyzed
identically to \cite{Bachant2015-JoT}---are shown in Fig.~\ref{fig:Ktransport}.
Due to the weaker blade vortex shedding, we see transport due to vertical
advection at this point in the wake is approximately 3 times lower than the
higher solidity UNH-RVAT. Note that direct comparison is somewhat invalid, since
the total measurement plane area is about 5\% lower for this experiment.
However, the differences observed are beyond this discrepancy. We also see
relatively lower levels of cross-stream turbulent transport thanks to the lack
of blade stall vortex shedding. These results may have interesting implications
regarding the application of turbines with lower power coefficient to possibly
improve overall array performance through enhanced transport of kinetic energy
from the free stream, though a detailed anaylsis of the downstream evolution and
turbine interaction will be necessary.

\begin{figure}[ht!]
\includegraphics[width=0.9\textwidth]{figures/K_trans_bar_graph}

\caption{{\bf Mean Kinetic Energy Transport.} Weighted average estimates for
    terms contributing to streamwise recovery of mean kinetic energy, multiplied by
    two due to implied symmetry.}

\label{fig:Ktransport}
\end{figure}

@@

We see that strut drag losses increase with tip speed ratio to the power 2--3,
which makes streamlined struts much more important for low solidity turbines,
given the inverse correlation between solidity and $\lambda_0$.
